\abstracttitle
% Single spacing can be turned on for the abstract
%
{\singlespacing
	% EIO pathway -- machine learning pathway
Due to the complexity of financial market and the interconnectedness and interdependencies of industry sectors in the economy, the price returns of each coupling stocks might have certain underlying economic link. Such behaviours can hardly be explained by traditional financial models and theories. This thesis study on the construction and topological properties of US study stock market with complex networks theory. In order to determine the directions of edges in the stock network, we first used the machine learning technique to predict the Granger causalities of the price return series between all stock pairs while concluded with unsuccessful results. In addition, another method of using economical transactions of Economic Input-Output (EIO) from Bureau of Economic Analysis (BEA) is proposed. The constructed directed-unweighted stock network is partitioned in communities and compared with Erdős–Rényi (ER) random network and Watts-Strogatz (WS) small-world network with the same number of nodes and edges and the constructed directed-weighted stock network is compared with undirected-weighted stock network which is constructed by the method of correlation coefficient of stock price return series as previous researches conducted. Further, through analysing the topological properties including out-degree and out-strength distribution, efficiencies, betweenness centrality and clustering coefficient of both of the directed stock networks, we find that the main topological properties such as small-world feature and power-law distribution of degrees are still exist as the conventional undirected stock networks follow. Suggestions towards financial market investment are provided based on the results of the study.
}

